\singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant reproductive traits determine interactions with floral visitors

### 2021-10-19 Manuscript/Manuscript.Rmd
parenthesis edit

Species can optimise their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can use. With the recent availability of large trait databases (e.g., TRY [@kattge2011] and COMPADRE [@salguero2015]), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; bruelheide2018; @carmona2021]. However, most studies have focused on vegetative traits such as leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] trade-offs with little or no attention given to reproductive traits [@evojtko2020; @roddy2021] which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success. For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively [@barrett2003; @moeller2017] and outcrossing levels are positively correlated with flower size [@goodwillie2010]. In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species’ reliance upon animal pollination (pollinator dependence) and its role in attracting pollinators [@ollerton2011; @rodger2021]. However, it is still unknown to what extent these different reproductive compromises determine plant-pollinator interactions.

@@

The additional model for both presence-absence ($marginal R2 = 0.29$; $conditional R2 = 0.19$) and visitation rate ($marginal R2 = 0.30$; $conditional R2 = 0.03$) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns and that the contrasting differences between presence-absence and visitation rate for bees on PC1 (Fig. 3a and Fig. 3d) were driven by the family Andrenidae which interacted more frequently on presence-absence interactions with plant species with low number of flower but large (Supplementary Fig. S8).

>>>>

Species can optimise their fitness through various life-history traits, yet trade-offs among those traits constrain the range of potential strategies that a species can use. With the recent availability of large trait databases (e.g., TRY @kattge2011 and COMPADRE @salguero2015), plant ecological strategies are being increasingly examined, and are facilitating the identification of global patterns and constraints in plant form and function [@salguero2016; @diaz2016; bruelheide2018; @carmona2021]. However, most studies have focused on vegetative traits such as leaf [@wright2004], wood [@chave2009], or root [@laughlin2021] trade-offs with little or no attention given to reproductive traits [@evojtko2020; @roddy2021] which are critical to plant life strategies that shape interactions with pollinators and ultimately determine plant reproductive success. For instance, short lived versus perennial species tend to have low versus high levels of outcrossing, respectively [@barrett2003; @moeller2017] and outcrossing levels are positively correlated with flower size [@goodwillie2010]. In addition, the presence of costly rewards (e.g., pollen or nectar) and showy flowers or floral displays can only be understood through consideration of plant species’ reliance upon animal pollination (pollinator dependence) and its role in attracting pollinators [@ollerton2011; @rodger2021]. However, it is still unknown to what extent these different reproductive compromises determine plant-pollinator interactions.

@@

The additional model for both presence-absence of interactions ($marginal R2 = 0.29$; $conditional R2 = 0.19$) and visitation rate ($marginal R2 = 0.30$; $conditional R2 = 0.03$) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns and that the contrasting differences between presence-absence and visitation rate for bees on PC1 (Fig. 3a and Fig. 3d) were driven by the family Andrenidae which interacted more frequently on presence-absence interactions with plant species with low number of flower but large (Supplementary Fig. S8).

### 2021-10-19 Manuscript/Manuscript.tex
parenthesis edit

Species can optimise their fitness through various life-history traits,
yet trade-offs among those traits constrain the range of potential
strategies that a species can use. With the recent availability of large
trait databases (e.g.,
TRY\textsuperscript{\protect\hyperlink{ref-kattge2011}{22}} and
COMPADRE\textsuperscript{\protect\hyperlink{ref-salguero2015}{23}}),
plant ecological strategies are being increasingly examined, and are
facilitating the identification of global patterns and constraints in
plant form and
function\textsuperscript{\protect\hyperlink{ref-salguero2016}{12},\protect\hyperlink{ref-diaz2016}{24},\protect\hyperlink{ref-carmona2021}{25}}.
However, most studies have focused on vegetative traits such as
leaf\textsuperscript{\protect\hyperlink{ref-wright2004}{26}},
wood\textsuperscript{\protect\hyperlink{ref-chave2009}{27}}, or
root\textsuperscript{\protect\hyperlink{ref-laughlin2021}{28}}
trade-offs with little or no attention given to reproductive
traits\textsuperscript{\protect\hyperlink{ref-roddy2021}{5},\protect\hyperlink{ref-evojtko2020}{29}}
which are critical to plant life strategies that shape interactions with
pollinators and ultimately determine plant reproductive success. For
instance, short lived versus perennial species tend to have low versus
high levels of outcrossing,
respectively\textsuperscript{\protect\hyperlink{ref-moeller2017}{9},\protect\hyperlink{ref-barrett2003}{30}}
and outcrossing levels are positively correlated with flower
size\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{31}}. In
addition, the presence of costly rewards (e.g., pollen or nectar) and
showy flowers or floral displays can only be understood through
consideration of plant species' reliance upon animal pollination
(pollinator dependence) and its role in attracting
pollinators\textsuperscript{\protect\hyperlink{ref-ollerton2011}{32},\protect\hyperlink{ref-rodger2021}{33}}.
However, it is still unknown to what extent these different reproductive
compromises determine plant-pollinator interactions.

@@

The additional model for both presence-absence (\(marginal R2 = 0.29\);
\(conditional R2 = 0.19\)) and visitation rate (\(marginal R2 = 0.30\);
\(conditional R2 = 0.03\)) for the most represented families of bees
showed that the family Apidae was the main driver of the observed
patterns and that the contrasting differences between presence-absence
and visitation rate for bees on PC1 (Fig. 3a and Fig. 3d) were driven by
the family Andrenidae which interacted more frequently on
presence-absence interactions with plant species with low number of
flower but large (Supplementary Fig. S8).

>>>>

Species can optimise their fitness through various life-history traits,
yet trade-offs among those traits constrain the range of potential
strategies that a species can use. With the recent availability of large
trait databases (e.g., TRY \protect\hyperlink{ref-kattge2011}{22} and
COMPADRE \protect\hyperlink{ref-salguero2015}{23}), plant ecological
strategies are being increasingly examined, and are facilitating the
identification of global patterns and constraints in plant form and
function\textsuperscript{\protect\hyperlink{ref-salguero2016}{12},\protect\hyperlink{ref-diaz2016}{24},\protect\hyperlink{ref-carmona2021}{25}}.
However, most studies have focused on vegetative traits such as
leaf\textsuperscript{\protect\hyperlink{ref-wright2004}{26}},
wood\textsuperscript{\protect\hyperlink{ref-chave2009}{27}}, or
root\textsuperscript{\protect\hyperlink{ref-laughlin2021}{28}}
trade-offs with little or no attention given to reproductive
traits\textsuperscript{\protect\hyperlink{ref-roddy2021}{5},\protect\hyperlink{ref-evojtko2020}{29}}
which are critical to plant life strategies that shape interactions with
pollinators and ultimately determine plant reproductive success. For
instance, short lived versus perennial species tend to have low versus
high levels of outcrossing,
respectively\textsuperscript{\protect\hyperlink{ref-moeller2017}{9},\protect\hyperlink{ref-barrett2003}{30}}
and outcrossing levels are positively correlated with flower
size\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{31}}. In
addition, the presence of costly rewards (e.g., pollen or nectar) and
showy flowers or floral displays can only be understood through
consideration of plant species' reliance upon animal pollination
(pollinator dependence) and its role in attracting
pollinators\textsuperscript{\protect\hyperlink{ref-ollerton2011}{32},\protect\hyperlink{ref-rodger2021}{33}}.
However, it is still unknown to what extent these different reproductive
compromises determine plant-pollinator interactions.

@@

The additional model for both presence-absence of interactions
(\(marginal R2 = 0.29\); \(conditional R2 = 0.19\)) and visitation rate
(\(marginal R2 = 0.30\); \(conditional R2 = 0.03\)) for the most
represented families of bees showed that the family Apidae was the main
driver of the observed patterns and that the contrasting differences
between presence-absence and visitation rate for bees on PC1 (Fig. 3a
and Fig. 3d) were driven by the family Andrenidae which interacted more
frequently on presence-absence interactions with plant species with low
number of flower but large (Supplementary Fig. S8).
